---
title: "SocCult"
output: html_document
date: "2024-05-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)
```

```{r}
# Load the data
df_cashbenefit <- read.csv("data_w_cashbenefit_2205.csv")
df_cashbonus <- read.csv("data_w_cashbonus_2205.csv")
df_baseline <- read.csv("data_wo_bonus_2205.csv")
```

```{r}
table(df_baseline$Children)
table(df_cashbonus$Children)
table(df_cashbenefit$Children)


#Print the percentage of children in each socio_economic_class
table(df_baseline$socio_economic_class)
table(df_cashbonus$socio_economic_class)
table(df_cashbenefit$socio_economic_class)


```

```
```{r}
#Count the TFR - so the total number of children diveded by the rows        
TFR_base <- sum(df_baseline$Children) / nrow(df_baseline)
TFR_cashbonus <- sum(df_cashbonus$Children) / nrow(df_cashbonus)
TFR_cashbenefit <- sum(df_cashbenefit$Children) / nrow(df_cashbenefit)
print(TFR_base)
print(TFR_cashbenefit)
print(TFR_cashbenefit)

#print text and mean
mean(df_baseline$Children)
mean(df_cashbonus$Children)
mean(df_cashbenefit$Children)

```

```{r}
#Print the average and quantiles of number of children born in each socio_economic_class
print("Baseline quantiles for socioeconiomic class:")
df_baseline %>%
    group_by(socio_economic_class) %>%
    summarise(mean_children = mean(Children),
              quantile_25 = quantile(Children, 0.25),
              quantile_75 = quantile(Children, 0.75))

print("Cashbonus quantiles for socioeconiomic class:")
df_cashbonus %>%
    group_by(socio_economic_class) %>%
    summarise(mean_children = mean(Children),
              quantile_25 = quantile(Children, 0.25),
              quantile_75 = quantile(Children, 0.75))

print("Cashbenefit quantiles for socioeconiomic class:")
df_cashbenefit %>%
    group_by(socio_economic_class) %>%
    summarise(mean_children = mean(Children),
              quantile_25 = quantile(Children, 0.25),
              quantile_75 = quantile(Children, 0.75))
```

```{r}

#Plot the number of children from each socio_economic_class
df_baseline$socio_economic_class <- as.factor(df_baseline$socio_economic_class)
ggplot(df_baseline, aes(x = socio_economic_class, y = Children)) + geom_boxplot()

df_cashbonus$socio_economic_class <- as.factor(df_cashbonus$socio_economic_class)
ggplot(df_cashbonus, aes(x = socio_economic_class, y = Children)) + geom_boxplot()

df_cashbenefit$socio_economic_class <- as.factor(df_cashbenefit$socio_economic_class)
ggplot(df_cashbenefit, aes(x = socio_economic_class, y = Children)) + geom_boxplot()



```

```{r}
print(colnames(df_cashbenefit))
```

```{r}

# Rename the columns to remove hyphens
df_baseline <- df_baseline %>%
  rename(
    "1519" = `X15.19`,
    "2024" = `X20.24`,
    "2529" = `X25.29`,
    "3034" = `X30.34`,
    "3539" = `X35.39`,
    "4044" = `X40.44`,
    "4549" = `X45.49`)
  
````

```{r}
# Reshape the data to long format
df_long <- pivot_longer(df_cashbonus, 
                        cols = c("1519", "2024", "2529", "3034", "3539", "4044", "4549"),
                        names_to = "Age_Group", values_to = "Number_of_Children")
df_expanded <- df_long %>%
  uncount(Number_of_Children)

# Convert 'socio_economic_class' to factor
df_expanded$socio_economic_class <- as.factor(df_expanded$socio_economic_class)

# Print df_expanded to ensure it's created correctly
print(head(df_expanded))

write.csv(df_expanded, "long_baseline_2205.csv")
````

```{r}

#Load the long datafiles
long_cashbenefit <- read.csv("long_cashbenefit_2205.csv")
long_cashbonus <- read.csv("long_cashbonus_2205.csv")
long_baseline <- read.csv("long_baseline_2205.csv")


ggplot(long_cashbenefit, aes(x = socio_economic_class, fill = Age_Group)) +
  geom_bar(position = "dodge") +
  labs(x = "Socio-economic Class", y = "Number of Children", fill = "Age Group") +
    labs(subtitle = "Number of Children Born in Each Age Group in Each Socio-economic Class",
    title = "Cash benefit pro natal policy") + 
     theme_minimal()

# Plot the percentage of children in each socio_economic_class in each age group
ggplot(long_cashbenefit, aes(x = socio_economic_class, fill = Age_Group)) +
    geom_bar(position = "fill") +
    # Add labels of percentage of children of each age group in each socio-economic class
  geom_text(stat = "count", aes(label = scales::percent(..count../tapply(..count.., ..x.., sum)[..x..])),
            position = position_fill(vjust = 0.5)) + 
               labs(x = "Socio-economic Class", y = "Percentage of Children", fill = "Age Group") +
    labs(subtitle = "Percentage of Children Born in Each Age Group in Each Socio-economic Class",
    title = "Cash benefit pro natal policy") +
    theme_minimal()


  #Print the number agents in each socio_economic_class
table(long_cashbenefit$socio_economic_class)
table(long_cashbonus$socio_economic_class)
table(long_baseline$socio_economic_class)
```

```{r}
library(dplyr)
library(ggplot2)

# Calculate percentages
df_percentage <- long_cashbenefit %>%
  group_by(socio_economic_class) %>%
  mutate(total_children_socio = sum(Children)) %>%
  group_by(socio_economic_class, Age_Group) %>%
  summarise(percentage = sum(Children) / first(total_children_socio) * 100) %>%
  ungroup()

# Plot the percentage of children in each socio-economic class in each age group
ggplot(df_percentage, aes(x = socio_economic_class, y = percentage, fill = Age_Group)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Socio-economic Class", y = "Percentage of Children", fill = "Age Group") +
  labs(subtitle = "Percentage of Children Born in Each Age Group in Each Socio-economic Class",
       title = "Cash benefit pro natal policy") +
  theme_minimal()

```

```{r}
print(df_percentage)
```

```{r}
# Merge the three dataframes and add a column to indicate the condition
df_all <- rbind(
  mutate(long_cashbenefit, condition = "Cashbenefit"),
  mutate(long_cashbonus, condition = "Cashbonus"),
  mutate(long_baseline, condition = "Baseline")
)
# Ensure socio_economic_class is a factor
df_all$socio_economic_class <- as.factor(df_all$socio_economic_class)
df_all$condition <- as.factor(df_all$condition)
df_all$Age_Group <- as.factor(df_all$Age_Group)

# calculate the number of children in each age group for each socio_economic class in each condition
df_new <- df_all %>%
  group_by(socio_economic_class, Age_Group, condition) %>%
  summarise(Children = sum(Children))

# change children to percentage of children in that condition
df_new <- df_new %>%
  group_by(condition) %>%
  mutate(percentage = Children / sum(Children) * 100) %>%
  ungroup()

#Make accumulated percentage of children over age groups
df_new <- df_new %>%
  group_by(condition) %>%
  mutate(acc_percentage = cumsum(percentage)) %>%
  ungroup()

write.csv(df_new, "df_long_combined_2205.csv")
```

```{r}
custom_colors <- c("1" = "blue", "2" = "skyblue", "3" = "black")
custom_linetypes <- c("Cashbenefit" = "solid", "Cashbonus" = "dashed", "Baseline" = "dotted")

# Line plot of the amount of children born in each age group for each condition
ggplot(df_new, aes(x = Age_Group, y = percentage, color = socio_economic_class, linetype = condition, group = interaction(condition, socio_economic_class))) +
  geom_line() +
  scale_color_manual(values = custom_colors) +
  scale_linetype_manual(values = custom_linetypes) +
  labs(x = "Age Group", y = "Percentage of Children", color = "Socio-economic Class", linetype = "Condition") +
  labs(subtitle = "Percentage of Children Born in each Condition, for each age group",
       title = "Comparing distribution of children born") +
  theme_minimal()


```

```{r}


```

```{r}


```